Quantum Semiprime Factorization: Leveraging Grover's Algorithm for Efficient Prime Decomposition

### 2025-04-13 LaTeX/paper.tex
Paper revised

  The objective of this research is to clearly demonstrate quantum advantage 
  by showing clear speed-up to solve the same problem at the same scale.

@@

  One of the major intentions for this paper is demonstration of the broad utility of Grover's 
  algorithm.%, and to provide a general reference
  %for how Grover's algorithm may be used to invert a given function.

  Furthermore, the longer-term goal is to identify the types of algorithms that 
  likewise may have significant quantum advantage based upon reversible functions.
  % Grover's algorithm can be used to provide a very efficient search, 
  % which is in essence a content addressable memory that works at a scale limited only by qubit scaling.

@@

  Semiprime factoring is known to have a high time complexity due to the nature of
  prime number generation with a sieve (filters out all non-primes) and trial division search.
  This problem in particular becomes complex for large size semiprimes commonly used in 
  encryption, which might be 4096 bits or more. 
  Even a 128-bit semiprime, which is the product of two 64-bit primes requires time complexity
  that is beyond polynomial, and therefore requires a parallel computer to solve today.

  This is important since the simplicity of multiplying two large primes enables fast encryption of data, 
  but the complexity of factoring semiprimes ensures privacy so that data can only be accessed by someone possessing a private key 
  (one of the primes that compose the semiprime used for encryption).

  Data privacy hinges on this one-way function, called a trap-door, where factoring 
  is beyond P complexity, but trivial if one possesses the required key.

@@

  The only safety now for encryption is scaling the key size (semiprime) to keep 
  it larger than the largest quantum computer number of qubits.

@@

  The idea of factoring 4096 or bigger is nearly impossible even with the largest parallel computers available~\cite{FergusonSchneier2003}.

@@

  If it can be verified that SP factoring with Grover's algorithm
  uses significantly less qubits than Shor's, has less error, or has less overhead,
  then the application of quantum semiprime factoring at a meaningful scale 
  will be feasible far sooner.

@@

  The exact number of iterations required varies on a case-by-case basis,
  but is typically expressed as follows: in a search for one matching input
  state, $\frac{\pi}{4}\sqrt{N}$ iterations are required, and in a search
  for $k$ valid input states, $\sqrt{\pi}{4}\cdot \sqrt{\frac{N}{k}}$
  iterations are required, where $N$ is the size of the search domain.

  In most cases, $N=2^n$, where $n$ is the number of bits needed to represent
  the target value. This is by no means a steadfast rule, and is meant as 
  a helpful starting point for any confused readers attempting to implement
  something similar themselves.

@@

  Shor's algorithm is the most well-known approach to prime factorization
  in quantum computing. However, there are many drawbacks to this approach,
  the most notable of which being the need to take measurements mid-circuit
  and essentially re-run with new values afterwards, which introduces a 
  significant amount of overhead. Even recently improved versions of Shor's
  algorithm still require a minimum of $2n+1$ qubits, and tend to be 
  extremely sensitive to noise, which leads to high error\cite{quantum_factoring,shor}.

  Furthermore, when it comes to more concrete applications of Shor's algorithm,
  a full-scale implementation of this algorithm to factor an $n$-bit number
  may require up to $5n+1$ qubits for accurate results, and require 
  on the order of $n^3$ operations~\cite{quantum_fac_efficient}.

@@

  This optimization from $N$ to $M$ allows the implementation to ignore
  the trivial prime factors $2$ and $3$, and requires fewer qubits than would
  otherwise be needed to search for prime factors of $N$.

  While this approach is admirable, it introduces a level of complexity 
  that may hinder a learner's understanding of the mechanics at work,
  so the implementation shown in section\ \ref{sec:Methodology} forgoes
  this abstraction from $N$ to $M$, and instead implements an oracle which
  searches directly for prime factors $a$ and $b$ of a semiprime $N$.

@@

  This use of Grover's algorithm involves three main parts: some function with
  one or multiple inputs, the oracle which filters for states in which the
  desired output was observed, and the diffuser, which increases the probability 
  of observing inputs from the correct state. An overview of this circuit is
  shown in Figure~\ref{fig:FIGURA1}.

  The oracle in Grover's algorithm performs a controlled operation which is meant
  to differentiate states $-|x,y\rangle$ that do result in the wanted target $z$ from 
  states $|x,y\rangle$ that do not result in the target $|z\rangle$.

  \begin{figure}[!ht]
  \centering
  % \includegraphics[width=6.0cm]{oracle_15.png}
  \includegraphics[width=5.0cm]{oracle_15.png}
  % \includegraphics[width=7.9cm]{oracle_15.png}
  \caption{Example circuit diagram for Grover's oracle marking entangled states 
  of the output register ($R_z=[q_0,q_{11}]$) via the target qubit ($q_{12}$), where
  $R_z=|15\rangle$.}\label{fig:FIGURA2}
  \end{figure}

@@

  Figure~\ref{fig:FIGURA2} shows an example of the oracle searching for the state $z=15$,
  or rather, $R_z=|001111\rangle$. To implement a circuit which can selectively target
  $z=15$, Toffoli gates (controlled-NOT) are applied on $R_z[0]$ and $R_z[1]$, 
  so that states where $R_z=|001111\rangle$ will temporarily be in
  state $R_z=|111111\rangle$, and the multi-controlled Toffoli gates\cite{multi_toffoli}
  will apply a NOT operation to the target qubit only for the desired states (where $z=15$). 
  These operations are then performed again, returning all but the target qubit 
  (which has the Z-gate applied) to their original states.

  The diffuser in Grover's algorithm (Figure~\ref{fig:FIGURA3}) can then increase the 
  probability of observing $-|x,y\rangle$ (states which have been marked by the oracle) 
  through a process known as inversion about the mean.

  \subsection{Semiclassical Arithmetic}

  As a proof of concept (prior to the release of~\cite{quantum_factoring}),
  a function $f(x,y)=x+y$ is defined such that $R_x=|x\rangle$, $R_y=|y\rangle$,
  and after performing $f(R_x,R_y)$, the output register $R_z$ shall be in the
  state $|x+y\rangle$.

  This approach was implemented in a similar manner to a classical full-adder,
  and has been observed to work in simulation with perfect accuracy~\cite{quantum_full_adder}.

  The semiclassical full-adder indeed works with Grover's algorithm. Input states were
  filtered to only measure inputs which resulted in a sum matching some given value.
  This is a trivial problem however, and only has potential usefulness due to the 
  relationship between multiplication and addition.

  Unfortunately, semiclassical multiplication requires direct measurement of $R_x$
  or $R_y$, which would collapse the superposition, so a different approach was
  needed.

@@

  The quantum fourier transform, QFT, is a very useful
  operation, typically used to transform a qubit register from the
  computational basis (binary) to the fourier basis (phase).  The QFT operation 
  is defined in great detail by Perez et al.~\cite{quantum_arithmetic}.

  To summarize, given a qubit register $R_x=|x\rangle$
  with $n$ qubits in the computational basis, there are $d=2^n$ potential states $|k\rangle$
  in $|x\rangle$ = $\{|0\rangle, |1\rangle, \ldots, |d-1\rangle\}$, the QFT operation in this
  basis would be defined as:

  \begin{equation}\label{eqn:QFT}
    QFT|x\rangle = \frac{1}{\sqrt{d}} \sum_{k=0}^{d-1}e^{i{\frac{2\pi x k}{d}}}|k\rangle
  \end{equation}

  *It is worth noting that in some cases, a QFT on some $R_x$ may require a series of SWAP
  operations $\{ SWP(q_0,q_{n-1}), SWP(q_1,q_{n-2}), \ldots, SWP(q_{\frac{n}{2}-1},q_{\frac{n}{2}})\}$
  in order for future arithmetic to work as expected.

  Once in the fourier basis, a specific number $x$ may be encoded by applying some
  rotation $\omega_k$ to qubits $q_k \in R_x | q_k=R_x[k]$. The rotation $\omega_k$ applied
  to each qubit $q_k$ can be defined as $\omega_k = \omega^{x k} = e^{i \frac{2\pi x k}{d}}$.

@@

  Addition of two qubit registers $R_a$ in state $|a\rangle$ and $R_b$ in state 
  $\phi(b)\rangle$ in the fourier basis 
  ($\phi ADD(|a\rangle, |b\rangle)=|a + b\rangle$) may be performed by applying
  controlled rotation gates $R_k$ which rotate qubits $b_j \in R_b$ by 
  $\omega_j=e^\frac{2\pi i}{2^j}$ about the $z$-axis for each 
  qubit $a_l | l \ge k, j=1+l-k$~\cite{quantum_arithmetic}.

  Multiplication in the quantum fourier domain can be done similarly. In terms of
  a quantum circuit generation implementation, simply treat the previously defined
  addition method as a function which adds the value of one register to another,
  and add some constant multiple $C$ as a parameter, adjusting $\omega_j$ to 
  $\omega_{j,C}=e^{C\cdot \frac{2\pi i}{2^j}}$. Now, to send the product of the two values in $R_x$
  and $R_y$ to $R_z$, do as follows: Add $|R_y|$ controlled $\phi ADD(R, q_c, C)$ gates to each
  $q_x$ in $R_x$, which will add the value of $|C\cdot x\rangle$ to $R_z$ where $C=2^u$ for
  each $q_u \in R_y \iff q_y = |1\rangle$. This is, in essence, performing repeated scaled addition from $R_x$ onto
  $R_z$, but the scaling factor is the powers of two corresponding to qubits in $R_y$, which
  in tandem is cumulatively equivalent to adding $|x\cdot y\rangle$ to $R_z$~\cite{quantum_arithmetic}.

@@

  After implementing the QFT arithmetic methods and the oracle and diffuser for
  grover's, it is trivial to implement a SP factoring circuit. Our implementation
  follows the diagram in Figure~\ref{fig:FIGURA1}, while substituting $F(x,y)$ for
  the $\phi MULT(R_x, R_y)$ operation described at the end of section 
  \ \ref{sec:qft_arithmetic}.

@@

  The temporary solution we found was to simply decrease the size of $R_x$ and $R_y$ to 
  $\lceil \log_2(\frac{N}{3})\rceil$, and set the size of $R_z$ to double that, to ensure no
  further overflow could occur.

@@

@@

This work is still in progress, but we have a working implementation of Grover's 
algorithm with the CUDA-Q simulation which can estimate the time to factor any 
semiprime up to the current scaling limits of the CUDA-Q simulation\cite{quantumfactoring_github}.

@@

  Due to the exploratory nature of this work, the initially sub-optimal nature of our 
  implementation is intentional, because it allows for a more direct view of the inputs
  and outputs in our circuit.

  For context, our current implementation uses $4 \lceil \log_2(\frac{N}{3})\rceil$ qubits
  to find the prime factors of an $n$-bit semiprime, whereas the design by S. Whitlock 
  et al.\cite{quantum_factoring} uses up to $2n-5$ qubits, which allowed them to simulate circuits which found
  prime factors of up to $35$-bit semiprimes, using up to a total of $65$ qubits. 
  The limiting factor for our simulations is VRAM, so it is expected that after implementing 
  the optimizations from S. Whitlock et al.,\ our simulations should be able to scale up to 
  $18$-bit semiprimes on the current equipment.

@@

Grover's algorithm has been demonstrated to be a highly versatile function,
able to invert almost any function that can be implemented on a quantum 
computer with inputs in superposition.

Quantum methods of SP factoring have been developing at a quick pace,
and it will most likely not be very long before practical examples
of quantum advantage may be seen.

@@

The current priority regarding the quantum circuit is to implement the optimizations
mentioned by S. Whitlock et al.\ to substitute the search term $N$ with the smaller
search term $M$, which should reduce the number of qubits needed from 
$4 \lceil \log_2(\frac{N}{3})\rceil$ to $2n-5$.

>>>>

  The greater objective of this research is to clearly demonstrate quantum advantage 
  by showing clear speed-up to solve the same problem at the same scale.

@@

  One major intention for this paper in particular is demonstration of the broad 
  utility of Grover's algorithm. %, and to provide a general reference
  %for how Grover's algorithm may be used to invert a given function.
  Furthermore, another long-term goal of this research is to identify the types of algorithms that 
  likewise may have significant quantum advantage based upon reversible functions.
  % Grover's algorithm can be used to provide a very efficient search, 
  % which is in essence a content addressable memory that works at a scale limited only by qubit scaling.

@@

  Semiprime factoring is known to have a high time complexity due to the nature of
  prime number generation with a sieve (filters out all non-primes) and trial division search.
  This problem in particular becomes complex for large size semiprimes commonly used in 
  encryption, which might be 4096 bits or more. 
  % Even a 128-bit semiprime, which is the product of two 64-bit primes requires time complexity
  % that is beyond polynomial, and therefore requires a parallel computer to solve today.

  % This is important since the simplicity of multiplying two large primes enables fast encryption of data, 
  % but the complexity of factoring semiprimes ensures privacy so that data can only be accessed by someone possessing a private key 
  % (one of the primes that compose the semiprime used for encryption).

  % Data privacy hinges on this one-way function, called a trap-door, where factoring 
  % is beyond P complexity, but trivial if one possesses the required key.

@@

  % The only safety now for encryption is scaling the key size (semiprime) to keep 
  % it larger than the largest quantum computer number of qubits.

@@

  % The idea of factoring 4096 or bigger is nearly impossible even with the largest parallel computers available~\cite{FergusonSchneier2003}.

@@

  The two most significant limitations to applied quantum computing are 
  qubit count and error rate. The algorithm displayed in this paper (and also by
  S. Whitlock, et al.~\cite{quantum_factoring}) demonstrates
  significant optimizations regarding the number of qubits required for semiprime
  factoring. It is important to note, however, that error rate increases dramatically
  in proportion to the number of gates applied, which may reduce the viability of
  these algorithms in practice. That being said, there are emerging quantum computing 
  hardware solutions which claim to have far better error-control methods than have yet
  been observed, such as the Majorana I~\cite{Aghaee2025}.

  If it can be verified that SP factoring with Grover's algorithm
  uses significantly less qubits than Shor's, has less error, or has less overhead,
  then the application of quantum semiprime factoring at a meaningful scale 
  may be feasible far sooner.

@@

  The exact number of iterations required varies on a case-by-case basis,
  but is typically expressed as follows: in a search for one matching input
  state, $\frac{\pi }{4}\sqrt{N}$ iterations are required, and in a search
  for $2$ valid input states, $\lfloor \frac{\pi }{4} \cdot 2^\frac{n_x + n_y}{2}\rfloor$
  iterations are required, where $N$ is the size of the search domain, and $n_x, n_y$ are
  the number of qubits needed to represent the prime factors $x$ and $y$, respectively~\cite{quantum_factoring}.

  % In most cases, $N=2^n$, where $n$ is the number of bits needed to represent
  % the target value. This is by no means a steadfast rule, and is meant as 
  % a helpful starting point for any confused readers attempting to implement
  % something similar themselves.

@@

  Shor's algorithm is the most well-known approach to prime factorization
  in quantum computing. While it is the fastest known quantum algorithm for 
  factoring semiprimes, it requires (in most cases) $5n+1$ qubits~\cite{quantum_fac_efficient},
  which is too large for problems of a practical size~\cite{quantum_factoring,shor}.

@@

  % This optimization from $N$ to $M$ allows the implementation to ignore
  % the trivial prime factors $2$ and $3$, and requires fewer qubits than would
  % otherwise be needed to search for prime factors of $N$.

  While this approach is admirable, it introduces a level of complexity 
  that may hinder a learner's understanding of the mechanics at work,
  so the implementation shown in section\ \ref{sec:Methodology} forgoes
  this abstraction from $N$ to $M$, and instead implements an oracle which
  searches directly for prime factors $a$ and $b$ of a semiprime $N$, without
  the additional pre-processing and post-processing steps.

@@

  This use of Grover's algorithm involves three main parts: some function with
  one or multiple inputs ($F(x,y)$ and $F^{\dagger}(x,y)$), the oracle which filters for states in which the
  desired output was observed, and the diffuser, which increases the probability 
  of observing inputs which match the previously marked state. An overview of this circuit is
  shown in Figure~\ref{fig:FIGURA1}. The $H$ operations on $R_x$ and $R_y$ are
  simply Hadamard operations, placing both registers in a uniform superposition.

  The oracle in Grover's algorithm performs a controlled operation which is meant
  to differentiate states $-|x,y\rangle$ that do result in the wanted target $z$ from 
  states $|x,y\rangle$ that do not result in the target $|z\rangle$ by conditionally 
  flipping the phase of the target qubit.

  \begin{figure}[!ht]
  \centering
  % \includegraphics[width=6.0cm]{oracle_15.png}
  \includegraphics[width=5.0cm]{oracle_15.png}
  % \includegraphics[width=7.9cm]{oracle_15.png}
  \caption{Example circuit diagram for Grover's oracle marking entangled states 
  of the output register ($R_z=[q_6,q_{11}]$) via the target qubit ($q_{12}$), where
  $R_z=|15\rangle = |001111\rangle$.}\label{fig:FIGURA2}
  \end{figure}

@@

  Figure~\ref{fig:FIGURA2} shows an example of the oracle searching for the state $z=15$,
  or rather, $R_z=|001111\rangle$. To implement a circuit which can selectively target
  $z=15$, NOT gates are applied on $R_z[0]$ and $R_z[1]$ (seen in the figure as $q_6,q_7$), 
  so that states where $R_z=|001111\rangle$ will then be in the
  state $R_z=|111111\rangle$, and the multi-qubit Toffoli gates\cite{multi_toffoli}
  will apply a NOT operation to the target qubit only for the desired states where $z=15$. 
  % $q_6$ and $q_7$ are chosen in particular because they are the $|0\rangle$ qubits in
  % the bitwise representation of $15$, and for the multi-qubit Toffoli to select this state,
  % all control qubits must be in state $|1\rangle$. 
  The NOT gates are again applied to $R_z$, returning it to state $|001111\rangle$,
  while the target qubit retains the phase flip in those corresponding states.

  To clarify, Toffoli gates have a target qubit (Seen as $q_{12}$ in Figure~\ref{fig:FIGURA2}, and `Tgt' in Figure~\ref{fig:FIGURA1}) 
  and two control qubits which must both be in state $|1\rangle$ for a NOT operation to be applied
  to the target qubit. There are methods of combining multiple Toffoli gates to behave
  as a multi-qubit Toffoli gate, which behaves similarly, but can have any number of control qubits ($[q_6,q_{11}]$),
  instead of being limited to just two\cite{multi_toffoli}.

  The diffuser in Grover's algorithm (Figure~\ref{fig:FIGURA3}) can then increase the 
  probability of observing $-|x,y\rangle$ (states which have been marked by the oracle) 
  through a process known as inversion about the mean~\cite{grover}.

  % \subsection{Semiclassical Arithmetic}

  % As a proof of concept (prior to the release of~\cite{quantum_factoring}),
  % a function $f(x,y)=x+y$ is defined such that $R_x=|x\rangle$, $R_y=|y\rangle$,
  % and after performing $f(R_x,R_y)$, the output register $R_z$ shall be in the
  % state $|x+y\rangle$.

  % This approach was implemented in a similar manner to a classical full-adder,
  % and has been observed to work in simulation with perfect accuracy~\cite{quantum_full_adder}.

  % The semiclassical full-adder indeed works with Grover's algorithm. Input states were
  % filtered to only measure inputs which resulted in a sum matching some given value.
  % This is a trivial problem however, and only has potential usefulness due to the 
  % relationship between multiplication and addition.

  % Unfortunately, semiclassical multiplication requires direct measurement of $R_x$
  % or $R_y$, which would collapse the superposition, so a different approach was
  % needed.

@@

  The quantum fourier transform, QFT, is a very useful
  operation, typically used to transform a qubit register from the
  computational basis (binary) to the fourier basis (phase).~\cite{quantum_arithmetic}.

  % To summarize, given a qubit register $R_x=|x\rangle$
  % with $n$ qubits in the computational basis, there are $d=2^n$ potential states $|k\rangle$
  % in $|x\rangle$ = $\{|0\rangle, |1\rangle, \ldots, |d-1\rangle\}$, the QFT operation in this
  % basis would be defined as:

  % \begin{equation}\label{eqn:QFT}
  %   QFT|x\rangle = \frac{1}{\sqrt{d}} \sum_{k=0}^{d-1}e^{i{\frac{2\pi x k}{d}}}|k\rangle
  % \end{equation}

  % *It is worth noting that in some cases, a QFT on some $R_x$ may require a series of SWAP
  % operations $\{ SWP(q_0,q_{n-1}), SWP(q_1,q_{n-2}), \ldots, SWP(q_{\frac{n}{2}-1},q_{\frac{n}{2}})\}$
  % in order for future arithmetic to work as expected.

  % Once in the fourier basis, a specific number $x$ may be encoded by applying some
  % rotation $\omega_k$ to qubits $q_k \in R_x | q_k=R_x[k]$. The rotation $\omega_k$ applied
  % to each qubit $q_k$ can be defined as $\omega_k = \omega^{x k} = e^{i \frac{2\pi x k}{d}}$~\cite{quantum_arithmetic}.

@@

  To summarize, the QFT domain allows addition to be done through rotations in another basis,
  and these rotations can be scaled by some constant $c$, which in practice also scales the 
  operand by $c$. Multiplication between values encoded in registers $R_x$ and $R_y$ can then be performed
  out-of-place into $R_z$ by conditionally adding the full value encoded in $R_x$ to $R_z$ for each qubit 
  $q_i$ in $R_y$, such that each of these register-wide additions are performed as controlled operations 
  which will only occur if $q_i=|1\rangle$, and that these additions are also scaled by $c=2^i$.

  The details of operations such as addition and multiplication are described at great
  lengths in the cited works, and interested readers are recommended to seek assistance
  there for further explanation~\cite{quantum_arithmetic}.

  % Addition of two qubit registers $R_a$ in state $|a\rangle$ and $R_b$ in state 
  % $\phi(b)\rangle$ in the fourier basis 
  % ($\phi ADD(|a\rangle, |b\rangle)=|a + b\rangle$) may be performed by applying
  % controlled rotation gates $R_k$ which rotate qubits $b_j \in R_b$ by 
  % $\omega_j=e^\frac{2\pi i}{2^j}$ about the $z$-axis for each 
  % qubit $a_l | l \ge k, j=1+l-k$~\cite{quantum_arithmetic}.

  % Multiplication in the quantum fourier domain can be done similarly. In terms of
  % a quantum circuit generation implementation, simply treat the previously defined
  % addition method as a function which adds the value of one register to another,
  % and add some constant multiple $C$ as a parameter, adjusting $\omega_j$ to 
  % $\omega_{j,C}=e^{C\cdot \frac{2\pi i}{2^j}}$. Now, to send the product of the two values in $R_x$
  % and $R_y$ to $R_z$, do as follows: Add $|R_y|$ controlled $\phi ADD(R, q_c, C)$ gates to each
  % $q_x$ in $R_x$, which will add the value of $|C\cdot x\rangle$ to $R_z$ where $C=2^u$ for
  % each $q_u \in R_y$ as a controlled operation requiring that $q_u = |1\rangle$. 
  % This is, in essence, performing repeated scaled addition from $R_x$ onto
  % $R_z$, but the scaling factor is the powers of two corresponding to qubits in $R_y$, which
  % in tandem is cumulatively equivalent to adding $|x\cdot y\rangle$ to $R_z$~\cite{quantum_arithmetic}.

@@

  After implementing the QFT arithmetic methods and the oracle and diffuser for
  grover's, it is trivial to implement a SP factoring circuit. Our implementation
  follows the diagram in Figure~\ref{fig:FIGURA1}, while substituting $F(x,y)$ for
  the $\phi MULT(R_x, R_y)$ operation described at the end of section 
  \ \ref{sec:qft_arithmetic}. Quantum computing operations can be represented as unitary
  matrices, so for any $MULT(R_x, R_y)$, the adjoint operation $MULT^\dagger(R_x,R_y)$ will 
  return all effected registers to their original states. The only change remaining after
  applying the multiplication adjoint is that which was done by the oracle; the entangled state
  of the target qubit has a flipped phase only in those states which resulted in our desired
  semiprime was computed as an output- the states in which our prime factors reside.

@@

  The temporary solution we found was to simply decrease the size of $R_x$ and $R_y$ to 
  $n_x=\lceil \log_2(\frac{N}{3})\rceil$, and set the size of $R_z$ to double that, to ensure no
  further overflow could occur. The size of $R_x$ and $R_y$ comes from the fact that $2$ and $3$ may
  be considered trivial factors, so no number $p \le N/3$ will result as a factor. 
  $\lceil\log_2(\frac{N}{3})\rceil$ is a simple computation to find the minimum number of bits required
  to represent any number $\le \frac{N}{3}$ in binary, as would be encoded in the qubit registers. The
  size of $R_z$ being double the size of $R_x$ or $R_y$ is based on the fact that the largest resultant
  multiple from any value in $R_x$ or $R_y$ can be approximated as ${(2^{n_x})}^2=2^{2\cdot n_x}$, which 
  in turn would require $2\cdot n_x$ bits to be safely represented.

@@

Our implementation of Quantum Semiprime Factoring with Grover's Algorithm is a fully
generalized circuit-building algorithm which can take any semiprime $N$ and return
unique prime factors $p$ and $q$ with accuracy asymptotically approaching $100\%$~\cite{quantumfactoring_github}. 
The program automatically calculates the required number of qubits for each register,
and initializes a custom instance of Grover's oracle to check for the provided value $N$.
The simulation uses statevectors to track the superposition of the circuit and apply
gates as their corresponding matrices. The circuits are run numerous times, then
correctness is checked across those runs to find the statistic for $\%$ acc, as seen 
in Figure~\ref{fig:FIGURC1}.

\begin{figure}[ht]\label{fig:FIGURC1}
\centering
\includegraphics[width=7.9cm]{results.png}
% \includegraphics[width=15.8cm]{grover_inversion.png}
% \includegraphics[width=14cm]{grover_inversion.png}
\caption{Example program output for $N=143$. The state of each qubit 
when measured is either $|1\rangle$ or $|0\rangle$, and registers are separated by underscores, as seen
after `Full result: $\dots$'}
\end{figure}

@@

@@

  For context, our current implementation uses $4 \lceil \log_2(\frac{N}{3})\rceil$ qubits
  to find the prime factors of an $n$-bit semiprime, whereas the design by S. Whitlock 
  et al.\cite{quantum_factoring} uses up to $2n-5$ qubits, which allowed them to simulate circuits which found
  prime factors of up to $35$-bit semiprimes, using up to a total of $65$ qubits. 
  The limiting factor for problem scaling in our simulations is memory, so it is expected that after implementing 
  the optimizations from S. Whitlock et al.,\ our simulations should be able to scale up to 
  $18$-bit semiprimes on the current equipment.

  To be blatantly clear, this Grover's-based implementation is more of a proof-of-concept than
  a truly preferrable design over Shor's. The longer time complexity of this implementation
  is expected to coincide with increased error if it were to be run on an actual quantum computer,
  and the implementation in it's current state has greater time complexity than current classical
  methods like GNSF~\cite{Bai2016,quantum_factoring}.

@@

Grover's algorithm is highly versatile, and has been implemented in a
generalized fashion, such that it is effectively plug-and-play, with the
only necessary parameter being the value to search for. Everything else is
determined by the function that is chosen for $F(x, \dots)$.

Despite the large time complexity, even this sub-optimal implementation requires
fewer qubits than Shor's algorithm, and constructing the program in such a 
generalized manner has made it trivial to use Grover's algorithm for nearly any other
such function that can take as input registers that are in uniform superposition.

@@

The current priority regarding the quantum circuit is to implement the optimizations
mentioned by S. Whitlock et al.\ to substitute the search term $N$ with the smaller
search term $M$, which should reduce the number of qubits needed from 
$4 \lceil \log_2(\frac{N}{3})\rceil$ to $2n-5$\ \cite{quantum_factoring}.
